%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Erik}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Olson}}}}} % Last name
	
	\vspace{5pt}
	
	{\huge Full-Stack Web Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	{5535 SE Madison St}\\
	{503.975.1208}\\
	{\href{mailto:eriklolson@zohomail.com}{eriklolson@zohomail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.375\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	{\href{https://linkedin.com/in/erik-olson-9b6bb7191}{linkedin.com/in/erik-olson-9b6bb7191}}\\
	{\href{https://github.com/eriklolson}{github.com/eriklolson}}\\
	{\href{https://bitbucket.org/cobrasolutions/}{bitbucket.org/cobrasolutions}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Objectives}
\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text

 % Required for vertically aligning minipages
 A position in the field of softwear development with special interests in web applications programming and data management.
 
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{SQL}{60}
		\baritem{Python}{70}
		\baritem{GIT}{68}
		\baritem{Flask}{95}
		\baritem{HTML/CSS}{90}
		\baritem{JavaScript}{47}
		\baritem{TailwindCSS}{80}
		\baritem{Terraform}{60}
	\end{barchart}
\end{minipage}

\begin{center}
	%\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
		\entry
		{2022 -- present}
		{Full-Stack Web Developer}
		{Slow Wine West}
		{Created back-end PostgreSQL database to store blog entries and user data. Developed webpages with TailwindCSS and
		Jinja templating. Created secure user login and register functions. Created Ubuntu Virtual Server from scratch to host
		website; configured Gunicorn WSGI server and Nginx reverse proxy. Configured DNS settings and secured website with 
		Certbot.\\
		
		Created eCommerce website with a Flask web app—{\href{https://github.com/eriklolson/flask-wineshop}{\itshape flask-wineshop}}—featuring 
		mock wine shop inventory. funcionalities of website include user account management, product search and views, shopping cart, order entry, and 
		account history. Wrote web scraper—{\href{https://github.com/eriklolson/python-wine-scraper}{\itshape python-wine-scraper}}—that 
		supplied the back-end database with mock wine products. Used Terraform to make cloud-native PostgreSQL database in 
		AWS Virtual Private Cloud.\\ \texttt{Flask}\slashsep\texttt{Python}\slashsep\texttt{Jinja2}\slashsep\texttt{TailwindCSS}\slashsep\texttt{Node.js}\slashsep\texttt{SQLAlchemy}\slashsep\texttt{KVM/QEMU}}
	\entry
		{2018 -- 2020}
		{Writing Coach}
		{Tutor.com}
		{I assisted clients in all stages of the writing process, from
		brainstorming and outlining, drafting and fine-tuning. Communicating clearly
		within time constraints, I ensure every session satisfied particular needs and
		learning styles of clients and met the requirements of their assignments.
		\\ \texttt{Linux}}
	\entry
		{2017 -- 2018}
		{Career Assistance Mentor}
		{Portland Public Schools}
		{Supported teachers in organizing and carrying out meaningful college and
		career exposure activities, from field trips to discussion panels, guest
		speakers to writing exercises.
		\\ \texttt{MS Word}\slashsep\texttt{Google Sheets}}
		
	\entry
		{2006 -- 2009}
		{Web Editor}
		{Moda Nova}
		{Edited and uploaded pictures from company database to website as batch file manager. Performed data loads and routine updates on an ongoing basis. 
		Performed updates to the SQL system as assigned by management.		
		Wrote SQL queries in MYSQL Server 2005.
		\\ \texttt{MYSQL}\slashsep\texttt{HTML}\slashsep\texttt{CSS}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\cvsect{Education/Certificates}
\begin{entrylist}
	\entry
		{2021}
		{CS50x}
		{Harvard}
		
	\entry
		{2020}
		{Fundamentals of Technical Writing}
		{Portland State University}

	\entry
		{2011 -- 20016}
		{Bachelor of Arts - English Language And Literature}
		{Portland State University}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	Project Links
%----------------------------------------------------------------------------------------
\cvsect{Projects}

\begin{minipage}[t]{0.45\textwidth}
	{\href{https://slowwinewest.com}{slowwinewest.com}} | {2022-present}
		\begin{itemize}
   			\item {\href{https://bitbucket.org/cobrasolutions/slow-wine-west}{bitbucket.org/cobrasolutions/slow-wine-west}}
		\end{itemize}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.45\textwidth}
		{\href{https://flaskwineshop.com}{flaskwineshop.com}} | {2022}
            \begin{itemize}
                \item {\href{https://github.com/eriklolson/flask-wineshop}{github.com/eriklolson/flask-wineshop}}
                \item {\href{https://github.com/eriklolson/python-wine-scraper}{github.com/eriklolson/python-wine-scraper}}
                \item {\href{https://bitbucket.org/cobrasolutions/terraform}{bitbucket.org/cobrasolutions/terraform}}
            \end{itemize}
            
\end{minipage}%


 
       
       
 %\begin{entrylist}
	 %\entry
	 %	{2022-present}
	 %	{\href{https://slowwinewest.com}{slowwinewest.com}}
 %{sdfsdf}

	 %\entry
	 %	{2022}
		 %{\href{https://flaskwineshop.com}{flaskwineshop.com}}
		 %{\href{https://github.com/eriklolson/flask-wineshop}{github.com/eriklolson/flask-wineshop}}

 %\end{entrylist}
%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	\textbf{Python} - proficient\\
	\textbf{SQL} - proficient\\
	\textbf{JavaScript} - competent\\
	\textbf{HTML/CSS} - proficient\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Environments}
	\textbf{Shell/Bash Scripting} - proficient\\
	\textbf{Python} - proficient\\
	\textbf{JIRA} - proficient\\
	\textbf{GIT} - proficient\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Infrastructure}
	\textbf{Docker} - proficient\\
	\textbf{AWS Cloud} - proficient\\
	\textbf{Nginx} - proficient\\
	\textbf{Terraform} - competent\\
\end{minipage}
%----------------------------------------------------------------------------------------
\end{document}
